---
title: "examplePackage: a template for writing packages in R."
author: "C A Pellett"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{examplePackage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
## The various macros in the `vignette` section of 
## the metadata block above are required in order to 
## instruct R how to build the vignette. 

## The `title` field and the `\VignetteIndexEntry` 
## should be consistent with your project.

## The `html_vignette` output type provides a custom style sheet 
## (and tweaks some options) to ensure that the resulting html is 
## as small as possible. 

## The `html_vignette` format:
## - Never uses retina figures
## - Has a smaller default figure size
## - Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

If you write a nice vignette, consider submitting it to the Journal of 
Statistical Software or The R Journal. 

This vignette is long form documentation of the examplePackage R package. 
Because this document is part of the distribution of the package, it needs to 
be compact. Larger components of a package can be shared on a project website.

The design goal of the examplePackage is to provide a bare-bones template 
that package developers can use to get started on a project. The material in 
examplePackage is meant to exemplify best practices when using devtools and
roxygen2 to create R packages. 

R packages are organized in a specific way so that they can be readily shared 
among R users. Organizing a project as an R package has many advantages, but 
the specific requirements of package development are a barrier for beginning
developers. Fortunately, tools such as the devtools package, the roxygen2 
package, and the RStudio integrated development environment (IDE) can be used to
automate some of the tasks of package development and documentation. One way the
process is streamlined by these tools is that almost all of the editing required
by the developer takes place in R files located in the R folder. 

In some cases, packages include data preparation scripts, which should be saved 
in the data-raw folder. 

This vignette is rendered from a .Rmd file located in the vignettes folder.

The README.md file shows up on the front page of the github (or bitbucket) 
repository. It should be edited as well.

Files in the test folder are probably edited also, but I haven't gotten there 
yet. Tests are important to better ensure the quality of the package and prevent
bugs from accumulating as the code is updated.


## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme 
you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images 
side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` 
in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, 
footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
